---
title: "Reproducible document"
author: "EBG"
format: html
editor: visual
---

## Basics of R

```{r}
1 + 1
```

## Setup code chunk

## About me

-   Erika B. Gram
-   Department of Clinical Research
-   University of Southern Denmark

I was born in **Sweden** and have lived in *Denmark* for 15 years.

## Simple code

```{r}
3 * 3
```

```{r setup}
#| message: false
#| warning: false
library(tidyverse)
post_meal_data <- read_csv2(
  here::here("data/post-meal-insulin.csv")
)

small_post_meal_data <- select(post_meal_data, id, Age, BMI, Group, auc_pg, auc_ins, glykemi)

tidier_post_meal_data <- small_post_meal_data |>
  rename(
    AUC_glucose = auc_pg,
    AUC_insulin = auc_ins
  ) |>
  filter(glykemi == 0) |>
  select(-glykemi)
```

## Showing the data

```{r}
post_meal_data
```

```{r}
glimpse(post_meal_data)
```

## Testing for Git

I don't think I follow what we are doing.

Again again

## Test 2

Will it work know?

```{r ggplot}
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

```{r}
#| fig-cap: "BMI results"
#| label: fig-BMI_histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

@fig-BMI_histo

## Exercise Discrete Plots

```{r}
#| fig-cap: Jabadabado
#| label: fig-jabadabado
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

See @fig-jabadabado for a cool plot

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = glykemi)) +
  geom_bar()
```

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```

## Putting two plots side by side

```{r}
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

```{r}
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

```{r side-by-side-figs}
#| fig-cap: "They are side by side!"
#| label: fig-bmi-glykemi
#| fig-subcap:
#| - "Distribution of BMI"
#| - "Number of those with glycemia"
#| layout-ncol: 2

ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()

ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

## Plotting two continous variables

```{r}
#| fig-cap: "Blodglukose og BMI"
#| label: fig-blodglukose_og_BMI
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```

@fig-blodglukose_og_BMI

## Pushing changes to remote

## Pulling changes locally

## Selecting data

```{r}
select(post_meal_data, Age)

select(post_meal_data, Age, BMI, Weight)

select(post_meal_data, -Group)

select(post_meal_data, starts_with("PG"))

select(post_meal_data, ends_with("DXA"))

select(post_meal_data, contains("0"))
```

## Renaming specific columns

```{r}
small_post_meal_data |>
  rename(AUC_glucose = auc_pg)

small_post_meal_data |>
  rename(AUC_glucose = auc_pg, AUC_insulin = auc_ins)
```

## Select and rename tasks

```{r}
# Task 1.
post_meal_data |>
  select(contains("OGTT"))

# Task 2.
post_meal_data |>
  select(contains(".."), -contains("...")) |>
  rename(
    Insulin.minus5.OGTT.X = Insulin..5.OGTT.X,
    P.Glucose.5.OGTT = P.Glucose..5.OGTT
  )


# Task 3.
basic_info <- select(post_meal_data, id, BMI, Length, Weight, Age)
rename(basic_info, Height = Length)

post_meal_data |>
  select(id, BMI, Length, Weight, Age) |>
  rename(Height = Length)
```

## Filtering data by row

```{r}
small_post_meal_data |>
  filter(glykemi == 1)

small_post_meal_data |>
  filter(BMI >= 25)

small_post_meal_data |>
  filter(Group == "CTR")
```

## Modify or column

```{r}
tidier_post_meal_data |>
  mutate(
    insuline_glucose_ratio = AUC_insulin / AUC_glucose,
    Group = if_else(Group == "CTR", "Control", "First-degree relative")
  )
```

```{r}
small_post_meal_data |>
  filter(Group == "CTR", BMI >= 25)

small_post_meal_data |>
  filter(Group == "CTR" | BMI >= 25)
```

## Practice filter and mutate

```{r}
# Task 1.
post_meal_data |>
  filter(BMI >= 20 & BMI <= 40 & Group == "FDR")

# Task 2.
post_meal_data |>
  mutate(
    percent_body_fat = (Fat.mass.DXA / Weight) * 100
  ) |>
  filter(percent_body_fat > 30)
```
