---
title: "Reproducible document"
author: "EBG"
format: html
editor: visual
---

## Basics of R

```{r}
1 + 1
```

## Setup code chunk

## About me

-   Erika B. Gram
-   Department of Clinical Research
-   University of Southern Denmark

I was born in **Sweden** and have lived in *Denmark* for 15 years.

## Simple code

```{r}
3 * 3
```

```{r setup}
#| message: false
#| warning: false
library(tidyverse)
post_meal_data <- read_csv2(
  here::here("data/post-meal-insulin.csv")
)
```

## Showing the data

```{r}
post_meal_data
```

```{r}
glimpse(post_meal_data)
```

## Testing for Git

I don't think I follow what we are doing.

Again again

## Test 2

Will it work know?

```{r ggplot}
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

```{r}
#| fig-cap: "BMI results"
#| label: fig-BMI_histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

@fig-BMI_histo

## Exercise Discrete Plots

```{r}
#| fig-cap: Jabadabado
#| label: fig-jabadabado
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```
See @fig-jabadabado for a cool plot

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = glykemi)) +
  geom_bar()
```

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```

## Putting two plots side by side

```{r}
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

```{r}
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

```{r side-by-side-figs}
#| fig-cap: "They are side by side!"
#| label: fig-bmi-glykemi
#| fig-subcap:
#| - "Distribution of BMI"
#| - "Number of those with glycemia"
#| layout-ncol: 2

ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()

ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

## Plotting two continous variables

```{r}
#| fig-cap: "Blodglukose og BMI"
#| label: fig-blodglukose_og_BMI
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) + 
  geom_point() +
  geom_smooth()
```
@fig-blodglukose_og_BMI

## Pushing changes to remote
